---
title: "foo"
author: "Aria Guo"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>")
```

This foo package is built based on the method in  [foofactor](https://github.com/STAT545-UBC/foofactors). The goal of this package is to practice how to develop an R package^[Write your own R package](http://stat545-ubc.github.io/packages00_index.html)]. I wrote two function in the package:

- `string_bind()`
- `letter_order()`

###Installation
```{r eval=FALSE}
devtools::install_github("AriaGuo/r-package-practise")
library(foo)
```

###First function

The first function **string_bind**is to bind two string characters into one string with unique values(default) or duplicated value. Based on the unit test result, this function works on any characters but with some exceptions. See notation in testthat.R for detail.

```{r eval=FALSE}
>string_bind("abc","bcde",method = "UNIQUE"")
[1] "abcde"
```

###Second function

The second function **letter_order** is to reorder input letter in a alphabetical order (default) or counter alphabetical order.Based on the unit test resutls, the function cannot handle white space, and letters with mixed capitalization very well. See examples in testthat.R

```{r eval=FALSE}
>letter_order("A,Z,U,O",normal.sort=TRUE)
[1] "A,O,U,Z"
```

